\speculake: Hiding Malware in Speculative Execution

### 2018-08-02 paper/architecture.tex

\speculake malware is comprised of two independent programs: a payload program,
and a trigger program. Both are installed on the victim's computer (e.g. via
trojan, remote exploit, or phishing), and must run simultaenously on the same
physical CPU. We note that the constraint of running programs on the same CPU is
not a signifcant burden: \texttt{taskset} can be used to limit a process to a
core, or if not available, the attacker can simply run multiple copies of the
trigger or payload program to coerce the OS scheduler to assign a
payload/trigger pair to the same core. We note that this is not a strict requirement
for the attacker as most OS schedulers will use round robin algrithms to assign 
tasks to processors -- eventually the trigger and payload will execute co-resident
on a single core.

>>>>

\speculake malware is comprised of two independent programs: a payload program,
and a trigger program. Both are installed on the victim's computer (e.g. via
trojan, remote exploit, or phishing), and must run simultaneously on the same
physical CPU. We note that the constraint of running programs on the same CPU is
not a significant burden: \texttt{taskset} can be used to limit a process to a
core, or if not available, the attacker can simply run multiple copies of the
trigger or payload program to coerce the OS scheduler to assign a
payload/trigger pair to the same core. We note that this is not a strict
requirement for the attacker as most OS schedulers will use round robin
algorithms to assign tasks to processors---eventually the trigger and payload
will execute co-resident on a single core.
